---
title: "Data Preprocessing_ANLY506"
author: "Bhuvaneshwari Meganathan"
date: "5/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(Hmisc)
library(dplyr)
library(tidyverse)
library(cluster)
library(factoextra)
library(ggplot2)
library(ggthemes)
library(devtools)
library(usethis)

```

#Reading data & summary    

```{r}
#Reading data
proj_data <- read_csv("G:/506/Project/Project DataSet1.csv")
View(proj_data)

#Summary of data
str(proj_data)
summary(proj_data)
glimpse(proj_data)

```

### /* ********************** Start of pre-analysis ******************************* */

```{r}


proj_data %>% count(gsub('[%]*[0-9]*',"",page),sort = TRUE)
proj_data %>% count(channel,sort = TRUE)
proj_data %>% count(company_name,sort = TRUE)
proj_data %>% count(job_views,sort = TRUE)
proj_data %>% count(job_apply_clicks,sort = TRUE)
proj_data %>% count(job_apply_success,sort = TRUE)

channl_job_suc <- proj_data %>% count(channel,job_apply_success,sort = TRUE)
#SEO job_apply_success
channl_job_suc[channl_job_suc$n < 12,]

rcorr(as.matrix(proj_data[sapply(proj_data,is.numeric)]),type = "pearson")

#boxplot(proj_data)
#cor(proj_data[sapply(proj_data,is.numeric)])
#is.numeric(proj_data[])

# Missing Value check

sapply(proj_data,function(x) sum(is.na(x)))

# We see missing values in 'Page', 'article_name', 'company_name'

# head(proj_data[is.na(proj_data$page),])



```


#Data Cleaning    

```{r}

# Remove article_name and company_name

proj_dat_cleaned <- proj_data[c(1:5,7,9:11)]

# filter only the page types "advice","profiles","jobs","NA","companies","tags","coaching","coaches","user"

page_type <- c("advice","profiles","jobs","NA","companies","tags","coaching","coaches","user")
proj_dat_cleaned <- (proj_dat_cleaned[proj_dat_cleaned$page %in% page_type,])

# Changing Page field to factor
proj_dat_cleaned$page = as.factor(proj_dat_cleaned$page)

#converting date into date format
proj_dat_cleaned$date = as.Date(proj_dat_cleaned$date)


capFirst <- function(s) {
  paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "")
}

proj_dat_cleaned$page <- capFirst(proj_dat_cleaned$page)
proj_dat_cleaned$channel <- capFirst(proj_dat_cleaned$channel)


#proj_dat_cleaned$weekday_page <- paste(weekdays(proj_dat_cleaned$date, abbreviate = TRUE),"-",proj_dat_cleaned$page)
#proj_dat_cleaned$weekday_channel <- paste(weekdays(proj_dat_cleaned$date, abbreviate = TRUE),"-",proj_dat_cleaned$channel)
#proj_dat_cln_grp -> proj_dat_cleaned %>% group_by(weekday_page)
#boxplot(proj_dat_cleaned[2:4])


```

The company_name is left as a factor for efficiency. It can be converted into character as needed.   
The columns: uv, sessions, page_views, job_views, job_apply_clicks, job_apply_success are already in "int" format. But if we were to convert all of them into numeric at once, we can follow the below steps:   




#Sessions by Page
```{r}
options(scipen = 999)

proj_dat_cleaned %>%
  group_by(page) %>%
  summarise(sessions = sum(sessions))%>%
  ggplot(aes(reorder(page,-sessions),sessions, fill = page))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(sessions,big.mark = ','),vjust=0))+
scale_y_continuous(labels = scales::comma)+
  labs(title = "Sessions by Page",
       x = "Page",
       y= "Sessions",
       fill = "Page") + theme_economist()+
  theme(plot.title = element_text(hjust = 0.5) ) + scale_fill_economist()
  
  
```

#Sessions by Channel
```{r}
options(scipen = 999)

proj_dat_cleaned %>%
  group_by(channel) %>%
  summarise(sessions = sum(sessions))%>%
  ggplot(aes(reorder(channel,sessions),sessions, fill = channel))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(sessions,big.mark = ','),hjust=0.35))+
scale_y_continuous(labels = scales::comma)+
  labs(title = "Sessions by Channel",
       x = "Channel",
       y= "Sessions",
       fill = "Channel") + theme_gdocs()+
  theme(plot.title = element_text(hjust = 0.5) ) + 
  scale_fill_discrete() + coord_flip()
  
  
```

#Sessions by day per channel
```{r}
options(scipen = 999)

# Sessions by Day per channel
proj_dat_cleaned %>%
  group_by(date,channel) %>%
  summarise(sessions = sum(sessions))%>%
  ggplot(aes(x =as.Date(date), y =sessions, color = channel))+
  geom_line() + facet_wrap(~channel, scales = "free")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Sessions by Day",
       x = "Date",
       y= "Sessions",
       fill = "Channel") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

# Sessions by Day
proj_dat_cleaned %>%
  group_by(date) %>%
  summarise(sessions = sum(sessions))%>%
  ggplot(aes(x =as.Date(date), y =sessions))+
  geom_line( color = "steel blue")+
  geom_smooth(method = "lm")+
scale_y_continuous(labels = scales::comma)+
  labs(title = "Sessions by Day",
       x = "Date",
       y= "Sessions") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

```
#Uv's by Channel
```{r}
options(scipen = 999)

proj_dat_cleaned %>%
  group_by(channel) %>%
  summarise(UV = sum(uv))%>%
  ggplot(aes(reorder(channel,UV),UV, fill = channel))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(UV,big.mark = ','),vjust=0))+
scale_y_continuous(labels = scales::comma)+
  labs(title = "Unique Visitors by Channel",
       x = "Channel",
       y= "Unique Visitors",
       fill = "Channel") + theme_gdocs()+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "None") + 
  scale_fill_discrete() + coord_flip()
  
  
```

#Uv's by Page
```{r}
options(scipen = 999)

proj_dat_cleaned %>%
  group_by(page) %>%
  summarise(UV = sum(uv))%>%
  ggplot(aes(reorder(page,-UV),UV, fill = page))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(UV,big.mark = ','),vjust=0, hjust = -0.00001))+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Unique Visitors by Page",
       x = "Page",
       y= "Unique Visitors",
       fill = "Page") + theme_economist()+
  theme(plot.title = element_text(hjust = 0.5) ) + scale_fill_economist()
  
  
```
#Uv's by day per channel
```{r}
options(scipen = 999)

# Uv's by Day per channel
proj_dat_cleaned %>%
  group_by(date,channel) %>%
  summarise(UV = sum(uv))%>%
  ggplot(aes(x =as.Date(date), y =UV, color = channel))+
  geom_line() + facet_wrap(~channel, scales = "free")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Unique Visitors by Day",
       x = "Date",
       y= "Unique Visitors",
       fill = "Channel") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

# Uv's by Day
proj_dat_cleaned %>%
  group_by(date) %>%
  summarise(UV = sum(uv))%>%
  ggplot(aes(x =as.Date(date), y =UV))+
  geom_line( color = "steel blue")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Unique Visitors by Day",
       x = "Date",
       y= "Unique Visitors") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

```

#Page Views by Channel
```{r}
options(scipen = 999)

proj_dat_cleaned %>%
  group_by(channel) %>%
  summarise(page_views = sum(page_views))%>%
  ggplot(aes(reorder(channel,page_views),page_views, fill = channel))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(page_views,big.mark = ','),hjust=0.43))+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Page Views by Channel",
       x = "Channel",
       y= "Page Views",
       fill = "Channel") + theme_gdocs()+
  theme(plot.title = element_text(hjust = 0.5) ) + 
  scale_fill_discrete() + coord_flip()

```

#Page Views  by day per Channel
```{r}
options(scipen = 999)


# Page Views by Day
proj_dat_cleaned %>%
  group_by(date) %>%
  summarise(page_views = sum(page_views))%>%
  ggplot(aes(x =as.Date(date), y =page_views))+
  geom_line( color = "steel blue")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Page Views by Day",
       x = "Date",
       y= "Page Views") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

#Page Views by day per channel
proj_dat_cleaned %>%
  group_by(date,channel) %>%
  summarise(page_views = sum(page_views))%>%
  ggplot(aes(x =as.Date(date), y =page_views, color = channel))+
  geom_line() + facet_wrap(~channel, scales = "free")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Page Views by Day",
       x = "Date",
       y= "Page Views",
       fill = "Channel") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

```


#Job Views by Channel
```{r}

options(scipen = 999)
proj_dat_cleaned %>%
  group_by(channel) %>%
  summarise(job_views = sum(job_views))%>%
  ggplot(aes(reorder(channel,job_views),job_views, fill = channel))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(job_views,big.mark = ','),hjust=0.43))+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Job Views by Channel",
       x = "Channel",
       y= "Job Views",
       fill = "Channel") + theme_gdocs()+
  theme(plot.title = element_text(hjust = 0.5) ) + 
  scale_fill_discrete() + coord_flip()
#+ bbc_style()

# Job Views by Page
proj_dat_cleaned %>%
  group_by(page) %>%
  summarise(job_views = sum(job_views))%>%
  ggplot(aes(reorder(page,-job_views),job_views, fill = page))+
  geom_bar(stat = "identity", width = 0.3) +
  geom_text(aes(label = format(job_views,big.mark = ','),vjust=0))+
scale_y_continuous(labels = scales::comma)+
  labs(title = "Job Views by Page",
       x = "Page",
       y= "Job Views",
       fill = "Page") + theme_economist()+
  theme(plot.title = element_text(hjust = 0.5) ) + scale_fill_economist()



```


#Job Views  by day per Channel
```{r}
options(scipen = 999)
# Page Views by Day
proj_dat_cleaned %>%
  group_by(date) %>%
  summarise(job_views = sum(job_views))%>%
  ggplot(aes(x =as.Date(date), y =job_views))+
  geom_line( color = "steel blue")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Job Views by Day",
       x = "Date",
       y= "Job Views") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

#Page Views by day per channel
proj_dat_cleaned %>%
  group_by(date,channel) %>%
  summarise(job_views = sum(job_views))%>%
  ggplot(aes(x =as.Date(date), y =job_views, color = channel))+
  geom_line() + facet_wrap(~channel, scales = "free")+
  geom_smooth(method = "lm")+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Job Views by Day",
       x = "Date",
       y= "Job Views",
       fill = "Channel") + theme_solarized()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(face="bold", color="#993333", 
                                   size=8, angle=30)) + 
  scale_fill_discrete()

```


#CORRELATION
```{r}
# Out of the whole dataset, only these variables will be considered.

variables = c(
    'uv', 
    'sessions',
    'page_views',
    'job_views',
    'job_apply_clicks',
    'job_apply_success'
  )

proj_dat_cleaned2 <- proj_dat_cleaned[, variables]
summary(proj_dat_cleaned2)

#Pearson method for a correlation table
round(cor(proj_dat_cleaned2, use="pairwise.complete.obs", method = "pearson"), 2)

#Price has the highest correlation to availability_365 according to the Pearson table

cor.test(proj_dat_cleaned2$job_views,proj_dat_cleaned2$uv, method = "pearson")
cor.test(proj_dat_cleaned2$job_views,proj_dat_cleaned2$sessions, method = "pearson")
cor.test(proj_dat_cleaned2$job_views,proj_dat_cleaned2$page_views, method = "pearson")
cor.test(proj_dat_cleaned2$job_views,proj_dat_cleaned2$job_apply_clicks, method = "pearson")
cor.test(proj_dat_cleaned2$job_views,proj_dat_cleaned2$job_apply_success, method = "pearson")


#Create Correltation plots for the dataset-
library(corrplot)
#cordata only created for corrplot
cordata = proj_dat_cleaned2
colnames(cordata) = c("job_views", "uv", "sessions", "page_views", "job_apply_clicks", "job_apply_success")
corrplot(cor(cordata), method="circle")


```

# **************  Scatterplots ***********************


```{r}

cleanup = theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line.x = element_line(color = 'black'),
                axis.line.y = element_line(color = 'black'),
                legend.key = element_rect(fill = 'white'),
                text = element_text(size = 15))

options(scipen = 999)

par(mfrow=c(2,2))


```


```{r}
# Session and Unique vistors
ggplot(proj_dat_cleaned, aes(uv, sessions)) + geom_point(aes(alpha = 0.2, size=2)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red") + 
    labs(title = "Scatterplot of Unique visitors and Session") + 
    labs(x = "Unique Visitors", y = "Sessions") +
    theme_economist() + scale_colour_economist()+
    cleanup

```


```{r}
# uv by Page views grouped by Page type


ggplot(proj_dat_cleaned, aes(uv, page_views)) + geom_point(aes(alpha = 0.2, size=2, colour = page)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red", aes(fill = page)) + 
    labs(title = "Scatterplot of Unique Visitor and page views by Page ") + 
    labs(x = "Unique Visitors", y = "Page Views")+
    cleanup

```

```{r}

# uv by Page views grouped by channel

ggplot(proj_dat_cleaned, aes(uv, page_views)) + geom_point(aes(alpha = 0.2, size=2, colour = channel)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red") + 
    labs(title = "Unique Visitors & page views by channel  ") + 
    labs(x = "Unique Visitors", y = "Page Views")+
    cleanup

```


```{r}
# uv by Job views
# Adding channel/page is not useful

ggplot(proj_dat_cleaned, aes(uv, job_views)) + geom_point(aes(alpha = 0.2, size=2)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red")  + 
    labs(title = "Scatterplot of Unique visitors and Job views") + 
    labs(x = "Unique Visitors", y = "Job Views")+
    cleanup


```


```{r}
# Job view and Job apply click by channel

ggplot(proj_dat_cleaned, aes(proj_dat_cleaned$job_views, proj_dat_cleaned$job_apply_clicks)) + geom_point(aes(colour = channel)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red")  + 
    labs(title = "Job views and Job apply click by Channel") + 
    labs(x = "Job Views", y = "Job apply Click")+
    cleanup


```

```{r}
# Job view and Job apply click by Page type
ggplot(proj_dat_cleaned, aes(proj_dat_cleaned$job_views, proj_dat_cleaned$job_apply_clicks)) + geom_point(aes(colour = page)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red")  + 
    labs(title = "Job views and Job apply click by Page") + 
    labs(x = "Job Views", y = "Job apply Click")+
    cleanup

```

```{r}
#  Job apply click and job application success by channel
ggplot(proj_dat_cleaned, aes(proj_dat_cleaned$job_apply_clicks, proj_dat_cleaned$job_apply_success)) + geom_point(aes(colour = channel)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red")  + 
    labs(title = "Job apply click & Job Apply success ") + 
    labs(x = "Job Apply Click", y = "Job Apply Success")+
    cleanup

```


```{r}
#  Job apply click and job application success by Page type
ggplot(proj_dat_cleaned, aes(proj_dat_cleaned$job_apply_clicks, proj_dat_cleaned$job_apply_success)) + geom_point(aes(colour = page)) + 
    guides(alpha=F,size=F) + stat_smooth(method = "lm", level = 0.95, colour = "red")  + 
    labs(title = "Job Apply clicks & Job apply Success by Page") + 
    labs(x = "Job Apply click", y = "Job Apply Success")+
    scale_fill_discrete() +
    cleanup

```

```{r}


ggplot(proj_dat_cleaned, aes(proj_dat_cleaned$job_apply_clicks, proj_dat_cleaned$job_apply_success, fill=proj_dat_cleaned$page)) + 
geom_boxplot()


m1 = lm(PRICE ~ SQFT, data = all_col)
summary(m1)


boxplot(proj_dat_cleaned$job_apply_clicks ~ proj_dat_cleaned$company_name, proj_dat_cleaned, xlab = "Company", ylab = "Job Apply Click")

ggplot(proj_dat_cleaned, aes(x=proj_dat_cleaned$page, y= proj_dat_cleaned$job_views)) + 
  geom_boxplot(outlier.colour="blue", outlier.size=4)


```


# Treat Outliers for unique visitors before scaling	


```{r}

# Unique visitors below 1.5*IQR to be replaced by 5 percentile and unique visitors above 1.5*IQR to be replaced by 95 percentile

qnt <- quantile(proj_dat_cleaned$uv, probs=c(.25, .75), na.rm = T)
caps <- quantile(proj_dat_cleaned$uv, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(proj_dat_cleaned$uv, na.rm = T)
proj_dat_cleaned$uv[proj_dat_cleaned$uv < (qnt[1] - H)] <- caps[1]
proj_dat_cleaned$uv[proj_dat_cleaned$uv > (qnt[2] + H)] <- caps[2]

```



# /* **** k-means clustering (By Page and Channel on unique visitors and job views) ****** */

```{r}


# Group data set on page and summarize on unique visitors and job views on mean
proj_dat_cln_grp_pg <- as.data.frame(proj_dat_cleaned %>%
  group_by(page) %>%
  summarise_at(vars(uv,job_views), funs(mean(., na.rm=TRUE))))

# Group data set on channel and summarize on unique visitors and job views on mean
proj_dat_cln_grp_chnl <- as.data.frame(proj_dat_cleaned %>%
  group_by(channel) %>%
  summarise_at(vars(uv,job_views), funs(mean(., na.rm=TRUE))))

# Make page and channel as rownames in respective dataset
rownames(proj_dat_cln_grp_pg) <- proj_dat_cln_grp_pg$page
rownames(proj_dat_cln_grp_chnl) <- proj_dat_cln_grp_chnl$channel
proj_dat_cln_grp_chnl <- proj_dat_cln_grp_chnl[2:3]
proj_dat_cln_grp_pg <- proj_dat_cln_grp_pg[2:3]

# scale dataset to standardize values for unique visitors and job views
k_clus_proj_dat <- scale(proj_dat_cln_grp_pg)
k_clus_proj_dat_chnl <- scale(proj_dat_cln_grp_chnl)

#distance <- get_dist(k_clus_proj_dat)
#fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))
#distance


#	Clusters for dataset grouped by page

set.seed(080620)

wss <- function(k) {
  kmeans(proj_dat_cln_grp_pg, k, nstart = 25 )$tot.withinss
}
# Compute and plot wss for k = 1 to k = 7
k.values <- 1:7
wss_values <- map_dbl(k.values, wss)
plot(k.values, wss_values,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

k3 <- kmeans(proj_dat_cln_grp_pg, centers = 3, nstart = 25)
k3
fviz_cluster(k3, data = proj_dat_cln_grp_pg)


# Clusters for dataset grouped by channel 

set.seed(070620)

wss_chnl <- function(k) {
  kmeans(proj_dat_cln_grp_chnl, k, nstart = 25 )$tot.withinss
}

# Compute and plot wss for k = 1 to k = 15
k.values_chnl <- 1:15

wss_values_chnl <- map_dbl(k.values_chnl, wss_chnl)

plot(k.values_chnl, wss_values_chnl,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

k3_chnl <- kmeans(proj_dat_cln_grp_chnl, centers = 3, nstart = 25)
k3_chnl
fviz_cluster(k3_chnl, data = proj_dat_cln_grp_chnl)


```


# Linear Model
```{r}

Model1  = lm(job_views~uv,data = proj_dat_cleaned)
summary(Model1)
summary(Model1)$adj.r.squared

Model2 <- lm(job_views~uv+ sessions,data = proj_dat_cleaned)
summary(Model2)
summary(Model2)$adj.r.squared

Model3 <- lm(job_views~uv+ sessions+ page_views,data = proj_dat_cleaned)
summary(Model3)
summary(Model3)$adj.r.squared

Model4 <- lm(job_views~uv+ sessions+ page_views+ job_apply_clicks,data = proj_dat_cleaned)
summary(Model4)
summary(Model4)$adj.r.squared

Model5  = lm(job_views~ uv+ sessions+ page_views + job_apply_clicks+ job_apply_success,data = proj_dat_cleaned)
summary(Model5)
summary(Model5)$adj.r.squared

#To test for Multicollinearity
summary(Model5, correlation = T)

# Individual pair-wise correlation is an indicator of multicollinearity. The correlation coeff of the  variables shows that each variables are not highly correlated as the value is not close to 1.
# Also multicollinearity exist when there is very high R squared ie more than 0.90 and coefficients are not significant according to their p-values. In our model R squared is 0.09, F statistic is significant 9468 and   p value is less than 0.05. The individual p value for most of the variables is significant. Hence there is no multicollinearity

#Comparing the models
anova(Model1, Model2, Model3, Model4, Model5) 

#Looking at the adj R squared Model4 provides an increase in the adj R squard value and is significant. Model 4 is the best model

```